%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Thapelo Tsotetsi
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Thapelo Tsotetsi CV}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Born in South Africa,}}{15 January 1988} % Birthplace and date


\NewEntry{full name}{Thapelo Tsotetsi} % Surname

\NewEntry{id number}{880115 5892 089} % ID Number

\NewEntry{email}{\href{mailto:thapelo.tsotetsi504@gmail.com}{thapelo.tsotetsi504@gmail.com}} % Email address

\NewEntry{github}{\href{https://github.com/tsotetsi}{https://github.com/tsotetsi}} % Github profile

\NewEntry{website}{\href{https://www.hackerrank.com/tsotetsithapelo}{https://www.hackerrank.com/tsotetsithapelo}} % Hackerrank profile

\NewEntry{phone}{(M) +27 (067) 022 0764} % Phone number(s)

\NewEntry{address}{9 Disa Road Belhar, Western Cape, ZA} % Address

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Goal}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{Gain fundamental experience by working across wide variety of projects.}\vspace{2em} % Goal text

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2020/01 Present}{ Coding Lecturer - Software Developer}

\Description{\MarginText{Lifechoices Coding Academy}The role involves teaching youth(18-25 years) how to program using Python, Flask, SQL, HTML, JS(Pure/React) and CSS. Created content(slides, handouts, exercises \& final projects) for the Backend languages. Worked on internal tools to improve efficiency. \\ 
 
\vspace{0.5em}

 Tech Stack : Python \ \ $\cdotp$\ \ JavaScript\ \ $\cdotp$\ \ Flask\ \ $\cdotp$\ \ MySQL/Sqlite\ \ $\cdotp$\ \ Git \ \ $\cdotp$\ \ Linux \ \ $\cdotp$\ \ Jira}

%------------------------------------------------

\NewEntry{2019/07 2019/12}{ Software Developer -- whereismyjojo}

\Description{\MarginText{Whereismyjojo}I relocated to Johannesburg because there was a promising business opportunity that I wanted to explore. Unfortunately, things didn't work out as planned after the JHB local elections. The project that I was working on was cancelled. The project involved building a platform that allows the department of water and sanitation to efficiently distribute water trucks with live tracking. \\ 
 
\vspace{0.5em}

 Tech Stack : Python \ \ $\cdotp$\ \ JavaScript\ \ $\cdotp$\ \ Django\ \ $\cdotp$\ \ React-Native\ \ $\cdotp$\ \ Git \ \ $\cdotp$\ \ HTML/CSS}

%------------------------------------------------

\NewEntry{2017/10 2019/06}{ Front-end Developer, \textsc{Zapper -- zapper.com}}

\Description{\MarginText{Zapper}I was responsible for building client applications for the Zapper mobile payment app. Responsibilities included: Integrating Back-end(API) with the Front-end, Communicate \& collaborate with product managers \& designers, Translate UI visuals on Zeplin to responsive websites, research, design, develop \& test new web app(s) for internal use, prepare \& deploy releases across different environments (QA, Staging \& Prod), investigate, reproduce \& fix reported bugs, refactor, redesign \& optimise current zapper codebase. \\ 
 
\vspace{0.5em}

 Tech Stack : PHP \ \ $\cdotp$\ \ JavaScript\ \ $\cdotp$\ \ CSS\ \ $\cdotp$\ \ MySQL\ \ $\cdotp$\ \ Git \ \ $\cdotp$\ \ Apache2 }

%------------------------------------------------

\NewEntry{2016/03 2017/10}{ Full-Stack Developer, \textsc{Byteorbit -- byteorbit.com}}

\Description{\MarginText{Byteorbit}I was involved in building web applications and RESTful API’s with Django rest-framework consumed by both AngularJS and mobile native apps. I worked on both the backend and frontend. \\ 
 
\vspace{0.5em}

 Tech Stack : Django\ \ $\cdotp$\ \ PostgreSQL\ \ $\cdotp$\ \ AngularJS\ \ $\cdotp$\ \ Amazon S3 \ \ $\cdotp$\ \ Bootstrap }

%------------------------------------------------

\NewEntry{2015/01 2016/01}{ Software Developer, \textsc{Textily -- textily.co.za}}

\Description{\MarginText{Textily}Developed USSD applications and RESTful API’s for USSD and SMS applications.. \\ 
 
\vspace{0.5em}

 Tech Stack : Django\ \ $\cdotp$\ \ PostgreSQL\ \ $\cdotp$\ \ VumiGO API\ \ $\cdotp$\ \ Twilio }

%------------------------------------------------

\NewEntry{2014/01 2014/12}{ Residence Subwarden, \textsc{UCT -- uct.ac.za}}

\Description{\MarginText{University of Cape Town}Developed residence room allocation web application while I was a Subwarden at residence. Students at UCT residence can now apply to be allocated rooms online. \\ 
 
\vspace{0.5em}

 Tech Stack : PHP\ \ $\cdotp$\ \ MySQL\ \ $\cdotp$\ \ Bootstrap\ \ $\cdotp$\ \ Bulk SMS Api }

%------------------------------------------------

\NewEntry{2014/01 2014/07}{ Software Developer - Intern, \textsc{praekelt.org}}

\Description{\MarginText{Praekelt Foundation}Built a Front-end UI prototype for Vumi campaign manager. \\ 
 
\vspace{0.5em}

 Tech Stack : VumiGO API\ \ $\cdotp$\ \ d3.js\ \ $\cdotp$\ \ AngularJS\ \ $\cdotp$\ \ Mocha }

%------------------------------------------------

\NewEntry{2013/06 2013/07}{ Software Developer - Intern, \textsc{Mxit -- mxit.co.za}}

\Description{\MarginText{Mxit}Built web application messages aggregator for Nelson Mandela (Madiba Wall). \\ 
 
\vspace{0.5em}

 Tech Stack : Redis\ \ $\cdotp$\ \ Mxit API\ \ $\cdotp$\ \ Bootstrap\ \ $\cdotp$\ \ NodeJS }

%------------------------------------------------

\NewEntry{2010/01 2013/12}{ Web Developer - Co-Founder, \textsc{orensa.co.za}}

\Description{\MarginText{Orensa Softwares}Participated in the full-life cycle of new web development projects. Provided technical support to end users. Was in charge of maintaining web hosting servers and services. \\ 
 
\vspace{0.5em}

 Tech Stack : PHP\ \ $\cdotp$\ \ MySQL\ \ $\cdotp$\ \ Bootstrap\ \ $\cdotp$\ \ JavaScript\ \ $\cdotp$\ \ Apache2 }

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\NewEntry{2010-2015}{University Of Cape Town, South Africa}

\Description{\MarginText{Bachelor of Science}Majors: Computer Science and Business Computing \\ 
Description: Data Structures and Algorithms. Project Management and Business processes. Game Development
with Java and Unity3D, C ++ applications and Machine Learning.\newline}

%------------------------------------------------

\NewEntry{Matric - 2006}{Mampoi High School, Free State, ZA}

\Description{\MarginText{Matriculation}Merit - Subjects $\cdotp$\ Maths, Physics, Biology, Geography, Sesotho and English.}

%------------------------------------------------

\vspace{0em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skills}\vspace{1em}

\Description{\MarginText{Intermediate}\textsc{Languages} -- Python, Java, PHP, JavaScript, C++, SQL, CSS, HTML5}

\Description{\MarginText{Intermediate}\textsc{DB’s \& DevOps} -- MySQL, PostgreSql, Redis, Travis CI, Docker, TFS, Jira, Git}

\Description{\MarginText{Intermediate}\textsc{Frameworks} -- Android, Django, Symfony, Laravel, Angular1, React-Native}


%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Awards}2013\ \ $\cdotp$\ \ Won Software Development Challenge organized by {\href{https://m.facebook.com/diakanyo.sita/photos/a.284989448336488/284989578336475/?type=3&source=48&__tn__=EH-R}{SITA}}}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\MarginText{Interests and Hobbies}Music, Sports, Computers, Opensource Softwares, Video Games}


%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{References}\vspace{1em}

\NewEntry{Mr Khoete}{ Software Developer (API), Zapper}

\Description{\MarginText{ Contact(s) }mail: {\href{mailto:leo.khoete@zapper.com}{leo.khoete@zapper.com}} | mobile: +2781 754 6737. \\}
 
\vspace{0.5em}

\NewEntry{Mr Ratshili}{ Frontend Developer , Discovery}

\Description{\MarginText{ Contact(s) }mail: {\href{mailto:ratshili.te@gmail.com}{ratshili.te@gmail.com}} | mobile: +2779 955 4850. \\}
 
\vspace{0.5em}

%------------------------------------------------


\end{cv}

\end{document}
